\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Brian Hill} \\ \vspace{1pt}
    \small 703-946-1545 $|$ \href{mailto:hillbr20@gmail.com}{\underline{hillbr20@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/brian-hill-0082161a3/}{\underline{LinkedIn}} $|$
    \href{https://github.com/TrojanPinata}{\underline{Github}} $|$
    \href{https://brianchill.us/}{\underline{brianchill.us/}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {Computer Engineering, BS}{Expected December 2024}
          \resumeItemListStart
            \resumeItem{Notable Courses: Circuit Analysis I, Comp Programming for Engr, Object-Oriented Programming, Continuous-Time Signals and Systems, Digital System Design, Differential Equations, Computer Organization}
            
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Intern}{Reston, VA}
      {CACI International Inc.}{May 2023 – Present}
      \resumeItemListStart
        \resumeItem{Modified and developed SQL scripts for conversion between government financial systems.}
        \resumeItem{Worked on Python-Selenium-based Automated testing tool for Momentum based software.}
        \resumeItem{Utilized government-based Agile approach to efficiently iterate on given requirements.}
        \resumeItem{Received public trust clearance by VA.}
      \resumeItemListEnd

    \resumeSubheading
      {Sales Associate and Print Specialist}{Manassas, VA}
      {The UPS Store}{November 2020 – Present}
      \resumeItemListStart
        \resumeItem{Managed Enterprise IT network and point of sales systems.}
        \resumeItem{Supervised high volume print jobs and designing methods to more efficiently sort and manage multiple enterprise grade printers.}
        \resumeItem{Worked in national and international logistics for major retail package services.}
        \resumeItem{Designed and printed customers personalized business advertisements.}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%-----------COMMUNITY AND LEADERSHIP-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Keyboard Design}{}
      {\href{brianchill.us/\#/Keyboard}{brianchill.us/\#/Keyboard}}{}
      \resumeItemListStart
        \resumeItem{Designed Schematic, PCB, and external housing for external Manufacturing.}
        \resumeItem{Added functionality to existing firmware and documented changes/code on Github.}
        \resumeItem{Wrote bill of materials and chose cost effective components for design which were implemented into final product.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Microcontroller Powered Video on OLED Screens}{}
      {\href{brianchill.us/\#/Oled}{brianchill.us/\#/Oled}}{}
      \resumeItemListStart
        \resumeItem{Developed software interface to transmit video over serial.}
        \resumeItem{Used OpenCV to process video and compressed data for transmission and low-level playback.}
      \resumeItemListEnd

    \resumeSubheading
      {Hardware-based Line Following Robot}{}
      {\href{brianchill.us/\#/LineFollower}{brianchill.us/\#/LineFollower}}{}
      \resumeItemListStart
        \resumeItem{Designed Opamp based platform to drive four motors - Controlled by photoresistor-LED, transceiver-receiver design.}
        \resumeItem{Integrated low-budget off the shelf components into design to satisfy budget requirements.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Java, PL/SQL, MATLAB, VHDL, JS/Web, Bash} \\
     \textbf{Professional Software}{: MS Office, Adobe CC, Fusion 360/Inventor, Xilinx Vivado, KiCAD/PSpice, Docker, Git, Jenkins, SQL Developer, Nginx/Apache, Node - ReactJS} \\
     \textbf{Operating Systems}{: Windows, Arch Linux, Ubuntu, Raspberry Pi OS, Fedora, Proxmox, ESXi} \\
     \textbf{Hardware Competencies}{: FPGAs, Microcontrollers, Elec.Testing Insts., Networking Devices} \\
    }}
 \end{itemize}

%-----------Awards-----------
\section{Awards \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {\textbf{IT Silver Medal} $|$ {June 2020}} \\ 
     {\textbf{GMU Tech Talent Awards} $|$ {Multiple Years}}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
